### 2015-01-20 src/analysis.Rnw
more explantion of minimal test suite required

Say the original set of mutants is given my $M$, then the reduced set of
mutants is given by $M_{strategy}$. The strategy choses $|M_{strategy}|$
mutants on its application. Test suite composed of test cases that
are able to kill any of the mutants of $M_{strategy}$ is given by
$T_{strategy}$. The total number of asserts on tests under $T_{strategy}$
is given by $asserts(T_{strategy})$. We find a minimal test suite that
is capable of killing all mutants under $M_{strategy}$ by a greedy strategy
of iteratively choosing the test cases with the largest amount of kills
for remaining mutants, and is given by $min(T_{strategy})$. Similarly,
for baseline, we use a strategy of randomly choosing the mutants from the
original set with number of mutants chosen same as the corresponding
number of mutants that the strategy under consideration chose.
That is, $|M_{strategy}| = |M_{random}|$. Given any set of tests $T$,
the total number of mutants that can be killed by the test cases in $T$
is given by $k(T)$, and those mutants that are covered by the test cases
are given by $c(T)$.

The \textit{test utility} is computed as the difference between the number
of non-redundant test cases the mutant selection achieved and the number of
non-redundant test cases of a random sample of same number of mutants.
The result is reported as a percentage of the non-redundant tests of the random
sample which is taken as the baseline. That is, test utility is given by
\[\left(\frac{|min(T_{strategy})|}{|min(T_{random})|}-1\right)\times 100.0\]

@@

\subsection{Statistical tests}
To compute the actual advantage gained by each of the different strategies, we
calculated the paired t-test between the number of test cases reported by the
strategy, and that of random selection of the same number of operators as
baseline, that is 
\[T.test\left(T_{strategy}\sim{}T_{random}\right)\]

>>>>

Suppose $M$ and $M_{strategy}$ denote the original set of mutants and  the reduced set of
mutants, respectively. 
% The strategy chooses $|M_{strategy}|$ mutants on its application. 
Test suite composed of test cases that 
are able to kill an $m$ where  $ m \in M_{strategy}$ is given by
$T_{strategy}$. The total number of \texttt{assert}s in $T_{strategy}$
is given by $asserts(T_{strategy})$. We find a minimal test suite that
is capable of killing all mutants under $M_{strategy}$ by a greedy algorithm
of iteratively choosing the test cases with the largest amount of kills
for remaining mutants, and is given by $min(T_{strategy})$. Similarly,
for baseline, we build set of randomly selected mutants $M_{random}$,
such that  $|M_{random}| = |M_{strategy}|$. Given any set of tests $T$,
the total number of mutants that can be killed by the test cases in $T$
is given by $k(T)$, and those mutants that are covered by the test cases
are given by $c(T)$.

The \textit{test utility} approximates the extra tests a selection strategy 
requires comparing a random sampling that suggest the same number of mutants.
We  compute it as the difference between the number
of non-redundant test cases the mutant selection achieved and the number of
non-redundant test cases of a random sample of same number of mutants. 
The result is reported as a percentage of the non-redundant tests of the random
sample which is taken as the baseline. That is, test utility is given by
\[\left(\frac{|min(T_{strategy})|}{|min(T_{random})|}-1\right)\times 100.0\]

Positive value test utility denotes that the strategy requires more tests
and negative test utility denotes that the strategy needs less test cases.
Values close to zero basically denote that the strategy rouphly suggest the 
same number of tests. Note that the comparison here is betweeen the size of
tests and it does not imply any subset relationship between test suites.

@@

\subsection{Statistical tests}
To compute the actual advantage gained by each of the different strategies, we
calculated the paired t-test between the number of test cases reported by the
strategy, and that of random selection of the same number of operators as
baseline, that is 
\[T.test\left(|T_{strategy}|\sim{}|T_{random}|\right)\]
